---
title: 'BIODATABASE: Extracting analysis data'
author: "Manu Chassot"
date: '`r format(Sys.time(), "%d %B %Y")`'
output: pdf_document
classoption: landscape
---
  
# Load the libraries
  
```{r load_libraries,echo=TRUE,eval=TRUE,results='hide',warning=FALSE,message=FALSE}
### Install/load devtools
if(!require(devtools)){
  install.packages("devtools", repos = "https://pbil.univ-lyon1.fr/CRAN/")
  suppressPackageStartupMessages(library(devtools,quietly = TRUE))
}

### Install/load lubripack
if(!require(lubripack)){
  install_github("espanta/lubripack")
  suppressPackageStartupMessages(library(lubripack,quietly = TRUE))
}

### Install/load libraries required for analysis
lubripack('RPostgreSQL','knitr','lubridate','openxlsx','data.table',silent = FALSE)
```

```{r document_parameters,echo=FALSE,results='hide',eval=TRUE}
### English
Sys.setlocale("LC_TIME", "en_US.UTF-8")

### PDF/DOC document parameters
knitr::opts_chunk$set(echo = FALSE,tidy.opts=list(width.cutoff=80),tidy=TRUE,size='footnotesize',fig.width=4.5,fig.height=4.5, fig.align = 'center')
```

# Connect to the database

```{r database_connection,echo=TRUE,eval=TRUE}
drv <- dbDriver("PostgreSQL")
con_emotion3_local <-  dbConnect(drv,user="postgres",dbname="emotion3",host="localhost")
```

# Amino acids

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="aa_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'TAA'
--AND so.tissue IN ('White muscle')
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_aa_raw_dataset,echo=TRUE,eval=TRUE}
aa_dataset <- dcast.data.table(as.data.table(na.omit(aa_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_aa_dataset,echo=TRUE,eval=TRUE}
write.xlsx(aa_dataset,file=paste('../XLS/datasets_exports/aa_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Dioxin

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="dioxin_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'Dioxin'
--AND so.tissue IN ('White muscle')
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_dioxin_raw_dataset,echo=TRUE,eval=TRUE}
dioxin_dataset <- dcast.data.table(as.data.table(na.omit(dioxin_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_dioxin_dataset,echo=TRUE,eval=TRUE}
write.xlsx(dioxin_dataset,file=paste('../XLS/datasets_exports/dioxin_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Fatty acids

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="fa_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
(CASE WHEN am.fraction_type LIKE 'PL' THEN am.measure_name || '_pl'
  ELSE (CASE WHEN am.fraction_type LIKE 'NL' THEN am.measure_name || '_nl'
  ELSE (CASE WHEN am.fraction_type LIKE 'TL' THEN am.measure_name || '_tl'
  ELSE am.measure_name END) END)END) AS measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'FA'
AND ( (am.measure_name LIKE ('%_p')) OR (am.measure_name LIKE ('%_c') ) )
ORDER BY so.fish_identifier,so.tissue,so.sample_position,sb.sample_origin_id,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_fa_raw_dataset,echo=TRUE,eval=TRUE}
fa_dataset <- dcast.data.table(as.data.table(na.omit(fa_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_fa_dataset,echo=TRUE,eval=TRUE}
write.xlsx(fa_dataset,file=paste('../XLS/datasets_exports/fa_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Mercury (dry weight)

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="hg_dry_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name || '_dw' AS measure_name,
ROUND(am.measure_value_avg::numeric,4) AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.measure_name LIKE 'THg_c'
AND am.analysis_sample_description LIKE 'dry bulk'
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_hg_dry_raw_dataset,echo=TRUE,eval=TRUE}
hg_dry_dataset <- dcast.data.table(as.data.table(na.omit(hg_dry_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_hg_dry_dataset,echo=TRUE,eval=TRUE}
write.xlsx(hg_dry_dataset,file=paste('../XLS/datasets_exports/hg_dry_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Mercury (wet weight)

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="hg_wet_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name || '_ww' AS measure_name,
ROUND(am.measure_value_avg::numeric,4) AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
LEFT OUTER JOIN public.fishes_environments_calculated fc ON (fc.fish_identifier = fish.fish_identifier)
WHERE am.measure_name LIKE 'THg_c'
AND am.analysis_sample_description LIKE 'wet bulk'
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_hg_wet_raw_dataset,echo=TRUE,eval=TRUE}
hg_wet_dataset <- dcast.data.table(as.data.table(na.omit(hg_wet_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_hg_wet_dataset,echo=TRUE,eval=TRUE}
write.xlsx(hg_wet_dataset,file=paste('../XLS/datasets_exports/hg_wet_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Lipid classes

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="lc_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'LC'
--AND so.tissue IN ('White muscle')
--AND am.analysis_sample_description LIKE 'wet bulk'
AND am.measure_name LIKE ('%_concentration')
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_lc_raw_dataset,echo=TRUE,eval=TRUE}
lc_dataset <- dcast.data.table(as.data.table(na.omit(lc_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_lc_dataset,echo=TRUE,eval=TRUE}
write.xlsx(lc_dataset,file=paste('../XLS/datasets_exports/lc_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Perfluorinated contaminants

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="pfc_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'PFC'
--AND so.tissue IN ('White muscle')
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_pfc_raw_dataset,echo=TRUE,eval=TRUE}
pfc_dataset <- dcast.data.table(as.data.table(na.omit(pfc_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_pfc_dataset,echo=TRUE,eval=TRUE}
write.xlsx(pfc_dataset,file=paste('../XLS/datasets_exports/pfc_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Proteins

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="prot_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'Prot'
--AND so.tissue IN ('White muscle')
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description
```

## Pivot the data set

```{r pivot_prot_raw_dataset,echo=TRUE,eval=TRUE}
prot_dataset <- dcast.data.table(as.data.table(na.omit(prot_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_prot_dataset,echo=TRUE,eval=TRUE}
write.xlsx(prot_dataset,file=paste('../XLS/datasets_exports/prot_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Stable isotopes

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="si_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name,
am.measure_value_avg AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'SI'
--AND am.analysis_sample_description NOT LIKE 'dry lipid-free'
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_si_raw_dataset,echo=TRUE,eval=TRUE}
si_dataset <- dcast.data.table(as.data.table(na.omit(si_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_si_dataset,echo=TRUE,eval=TRUE}
write.xlsx(si_dataset,file=paste('../XLS/datasets_exports/si_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Metallic contaminants (dry weight)

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="tm_dry_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name || '_dw' AS measure_name,
--ROUND(CASE WHEN am.analysis_sample_description LIKE 'dry bulk' THEN am.measure_value_avg ELSE am.measure_value_avg * 4::double precision END::numeric,4) AS measure_value
ROUND(am.measure_value_avg::numeric,4) AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'TM'
AND am.analysis_sample_description LIKE 'dry bulk'
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_tm_dry_raw_dataset,echo=TRUE,eval=TRUE}
tm_dry_dataset <- dcast.data.table(as.data.table(na.omit(tm_dry_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_tm_dry_dataset,echo=TRUE,eval=TRUE}
write.xlsx(tm_dry_dataset,file=paste('../XLS/datasets_exports/tm_dry_dataset_',Sys.Date(),'.xlsx',sep=''))
```

# Metallic contaminants (wet weight)

## Extract raw data set from the database

```{sql,connection=con_emotion3_local,include=TRUE,cache=FALSE,echo=TRUE,eval=TRUE,output.var="tm_wet_rawdata"}
SELECT so.fish_identifier,
so.tissue,
so.sample_position,
sb.sample_origin_id AS sample_identifier,
am.sample_id AS subsample_identifier,
am.analysis_sample_description,
am.measure_name || '_ww' AS measure_name,
--ROUND(CASE WHEN am.analysis_sample_description LIKE 'wet bulk' THEN am.measure_value_avg ELSE am.measure_value_avg / 4::double precision END::numeric,4) AS measure_value
ROUND(am.measure_value_avg::numeric,4) AS measure_value
FROM analysis_tables.analysis_measures_over_analysis_replicates am
INNER JOIN public.sample_bank sb ON (am.sample_id = sb.sample_id)
INNER JOIN public.samples_origin so ON (sb.sample_origin_id = so.sample_origin_id)
INNER JOIN public.fish ON (fish.fish_identifier = so.fish_identifier)
WHERE am.analysis_type LIKE 'TM'
AND am.analysis_sample_description LIKE 'wet bulk'
ORDER BY so.fish_identifier,so.tissue,so.sample_position,am.sample_id,am.analysis_sample_description;
```

## Pivot the data set

```{r pivot_tm_wet_raw_dataset,echo=TRUE,eval=TRUE}
tm_wet_dataset <- dcast.data.table(as.data.table(na.omit(tm_wet_rawdata)),fish_identifier+tissue+sample_position+sample_identifier+subsample_identifier+analysis_sample_description~measure_name,value.var = 'measure_value')
```

## Export the data set

```{r export_tm_wet_dataset,echo=TRUE,eval=TRUE}
write.xlsx(tm_wet_dataset,file=paste('../XLS/datasets_exports/tm_wet_dataset_',Sys.Date(),'.xlsx',sep=''))
```





```{r disconnect_emotiondb,echo=FALSE,results='hide',include='FALSE',eval=TRUE}
dbDisconnect(con_emotion3_local)
```
