---
title: 'BIODATABASE: Loading reference tables'
author: 'Manu Chassot'
date: "`r format(Sys.time(), '%d %B %Y')`"
classoption: 'landscape'
---

```{r load_libraries,echo=TRUE,eval=TRUE,results='hide',warning=FALSE,message=FALSE}
### Extend Java memory for XLConnect
#options(java.parameters = "-Xmx1024m")
options(java.parameters = "-Xmx2048m")
#options(java.parameters = "-Xmx4g" )

### Install/load devtools
if(!require(devtools)){
  install.packages("devtools", repos = "https://pbil.univ-lyon1.fr/CRAN/")
  suppressPackageStartupMessages(library(devtools,quietly = TRUE))
}

### Install/load lubripack
if(!require(lubripack)){
  install_github("espanta/lubripack")
  suppressPackageStartupMessages(library(lubripack,quietly = TRUE))
}

### Install/load libraries required for analysis
lubripack('RPostgreSQL','knitr','lubridate','XLConnect',silent = FALSE)
```

```{r document_parameters,echo=FALSE,results='hide',eval=TRUE}
### English
Sys.setlocale("LC_TIME", "en_US.UTF-8")

### PDF/DOC document parameters
knitr::opts_chunk$set(echo = FALSE,tidy.opts=list(width.cutoff=80),tidy=TRUE,size='footnotesize',fig.width=4.5,fig.height=4.5, fig.align = 'center')
```

# Connect to the database

```{r database_connection,echo=TRUE,eval=TRUE}
drv <- dbDriver("PostgreSQL")
con_emotion3_local <-  dbConnect(drv,user="postgres",dbname="emotion3",host="localhost")
```

# Read metadata from spreadsheet

```{r read_ddd,echo=TRUE,eval=FALSE}
DDD <- XLConnect::loadWorkbook("../XLS/DDD_Database.xls", create = FALSE)
```

# 1- Anchored Fish Aggregating Devices

```{r afads,echo=TRUE,eval=FALSE}
afad <- readWorksheet(DDD,sheet='AFAD')

### Save in temp to allow for insertion in the database
write.table(afad,file='/tmp/afad.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.afad
send.references.tables.afad <- dbSendQuery(con_emotion3_local,
paste0("COPY references_tables.afad FROM '/tmp/afad.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 2- Amino-acids list

```{r amino_acids,echo=TRUE,eval=FALSE}
amino_acids <- readWorksheet(DDD,"AMINO_ACIDS")

### Save in temp to allow for insertion in the database
write.table(amino_acids,file='/tmp/amino_acids.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.amino_acids
send.references.tables.amino_acids <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.amino_acids FROM '/tmp/amino_acids.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 3- Analysis groups

```{r analysis,echo=TRUE,eval=FALSE}
analysis <- readWorksheet(DDD,"ANALYSIS")

### Save in temp to allow for insertion in the database
analyis_groups <- unique(analysis[,c("analysis_group","desc_analysis_group")])
analyis_groups <- analyis_groups[order(analyis_groups$analysis_group),]
write.table(analyis_groups,file='/tmp/analysis_groups.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_groups
send.references.tables.analyis_groups <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_groups FROM '/tmp/analysis_groups.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 4- Analysis laboratories

```{r analysis_lab,echo=TRUE,eval=FALSE}
### Extract spreadsheet ANALYSIS_LAB
analysis_lab <- readWorksheet(DDD,"ANALYSIS_LAB")

### Save in temp to allow for insertion in the database
write.table(analysis_lab,file='/tmp/analysis_lab.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_lab
send.references.tables.analyis_lab <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_lab FROM '/tmp/analysis_lab.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 5- Matching between groups of analysis and analysis types

```{r analysis_matching_groups,echo=TRUE,eval=FALSE}
analysis_matching_groups <- unique(analysis[,c('analysis_group','analysis')])
names(analysis_matching_groups)[2] <- "analysis_type"

### Save in temp to allow for insertion in the database
write.table(analysis_matching_groups,file='/tmp/analysis_matching_groups.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_matching_groups
send.references.tables.analyis_matching_groups <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_matching_groups FROM '/tmp/analysis_matching_groups.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 6- Analysis modes

```{r analysis_modes,echo=TRUE,eval=FALSE}
analysis_modes <- readWorksheet(DDD,"ANALYSIS_MODE")

### Save in temp to allow for insertion in the database
write.table(analysis_modes,file='/tmp/analysis_modes.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_modes
send.references.tables.analyis_modes <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_modes FROM '/tmp/analysis_modes.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 7- Analysis replicates

```{r analysis_replicate,echo=TRUE,eval=FALSE}
analysis_replicate <- readWorksheet(DDD,"ANALYSIS_REPLICATE")

### Save in temp to allow for insertion in the database
write.table(analysis_replicate,file='/tmp/analysis_replicate.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_replicate
send.references.tables.analyis_replicate <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_replicate FROM '/tmp/analysis_replicate.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 8- Analysis sample description

```{r analysis_sample_description,echo=TRUE,eval=FALSE}
analysis_sample_description <- readWorksheet(DDD,"ANALYSIS_SAMP_DESCRIPTION")

### Save in temp to allow for insertion in the database
write.table(analysis_sample_description,file='/tmp/analysis_sample_description.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_sample_description
send.references.tables.analyis_sample_description <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_sample_description FROM '/tmp/analysis_sample_description.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 9- Analysis types

```{r analysis_types,echo=TRUE,eval=FALSE}
analysis_types <- unique(analysis[,c('analysis','desc_analysis')])
### Extract each component of analysis$desc_analysis from cut at '\n' and get first element
analysis_types$desc_analysis <- unlist(lapply(strsplit(analysis_types$desc_analysis,split = "\n"), function(l) l[[1]]))

### Save in temp to allow for insertion in the database
write.table(analysis_types,file='/tmp/analysis_types.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.analysis_types
send.references.tables.analyis_types <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.analysis_types FROM '/tmp/analysis_types.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 10- Atresia stages

```{r atresia,echo=TRUE,eval=FALSE}
atresia <- readWorksheet(DDD,"ATRESIA")

### Save in temp to allow for insertion in the database
write.table(atresia,file='/tmp/atresia.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.atresia
send.references.tables.atresia <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.atresia FROM '/tmp/atresia.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 11- Certified reference materials

```{r certified_reference_materials,echo=TRUE,eval=FALSE}
crm <- readWorksheet(DDD,"CRM")

### Save in temp to allow for insertion in the database
write.table(crm,file='/tmp/crm.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.crm
send.references.tables.crm <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.crm FROM '/tmp/crm.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 12- Derivatization modes

```{r derivatization_mode,echo=TRUE,eval=FALSE}
derivatization_mode <- readWorksheet(DDD,"DERIVATIZATION_MODE")

### Save in temp to allow for insertion in the database
write.table(derivatization_mode,file='/tmp/derivatization_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.vessel_storage
send.references.tables.derivatization_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.derivatization_mode FROM '/tmp/derivatization_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 13- Drying modes

```{r drying_mode,echo=TRUE,eval=FALSE}
drying_mode <- readWorksheet(DDD,"DRYING_MODE")

### Save in temp to allow for insertion in the database
write.table(drying_mode,file='/tmp/drying_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.atresia
send.references.tables.drying_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.drying_mode FROM '/tmp/drying_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 14- Extraction modes

```{r extraction_mode,echo=TRUE,eval=FALSE}
extraction_mode <- readWorksheet(DDD,"EXTRACTION_MODE")

### Save in temp to allow for insertion in the database
write.table(extraction_mode,file='/tmp/extraction_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.extraction_mode
send.references.tables.extraction_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.extraction_mode FROM '/tmp/extraction_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 15- Fatty acids list

```{r fatty_acids,echo=TRUE,eval=FALSE}
fatty_acids <- readWorksheet(DDD,"FATTY_ACIDS")

### Save in temp to allow for insertion in the database
write.table(fatty_acids,file='/tmp/fatty_acids.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.fatty_acids
send.references.tables.fatty_acids <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.fatty_acids FROM '/tmp/fatty_acids.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 16- Fishing modes

```{r fishing_mode,echo=TRUE,eval=FALSE}
fishing_mode <- readWorksheet(DDD,"FISHING_MODE")

### Save in temp to allow for insertion in the database
write.table(fishing_mode,file='/tmp/fishing_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.fishing_mode
send.references.tables.fishing_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.fishing_mode FROM '/tmp/fishing_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 17- Fishing gears

```{r gear,echo=TRUE,eval=FALSE}
gear <- readWorksheet(DDD,"GEAR")

### Save in temp to allow for insertion in the database
write.table(gear,file='/tmp/gear.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.gear
send.references.tables.gear <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.gear FROM '/tmp/gear.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 18- Grinding modes

```{r grinding_mode,echo=TRUE,eval=FALSE}
grinding_mode <- readWorksheet(DDD,"GRINDING_MODE")

### Save in temp to allow for insertion in the database
write.table(grinding_mode,file='/tmp/grinding_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.grinding_mode
send.references.tables.grinding_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.grinding_mode FROM '/tmp/grinding_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 19- Landing sites

```{r landing,echo=TRUE,eval=FALSE}
landing <- readWorksheet(DDD,"LANDING")

### Save in temp to allow for insertion in the database
write.table(landing,file='/tmp/landing.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.landing
send.references.tables.landing <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.landing FROM '/tmp/landing.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 20- Macroscopic maturity stages [visual exam]

```{r macro_maturity,echo=TRUE,eval=FALSE}
macro_maturity <- readWorksheet(DDD,"MACRO_MATURITY")

### Save in temp to allow for insertion in the database
write.table(macro_maturity,file='/tmp/macro_maturity.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.macro_maturity
send.references.tables.macro_maturity <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.macro_maturity FROM '/tmp/macro_maturity.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 21- Microscopic maturity stages [histology]

```{r micro_maturity_stage,echo=TRUE,eval=FALSE}
micro_maturity_stage <- readWorksheet(DDD,"MICRO_MATURITY")

### Save in temp to allow for insertion in the database
write.table(micro_maturity_stage,file='/tmp/micro_maturity_stage.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.micro_maturity
send.references.tables.micro_maturity_stage <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.micro_maturity_stage FROM '/tmp/micro_maturity_stage.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 22- Minerals

```{r minerals,echo=TRUE,eval=FALSE}
minerals <- readWorksheet(DDD,"MINERALS")

### Save in temp to allow for insertion in the database
write.table(minerals,file='/tmp/minerals.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.micro_maturity
send.references.tables.minerals <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.minerals FROM '/tmp/minerals.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 23- Oceans

```{r ocean,echo=TRUE,eval=FALSE}
ocean <- readWorksheet(DDD,"OCEAN")

### Save in temp to allow for insertion in the database
write.table(ocean,file='/tmp/ocean.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.ocean
send.references.tables.ocean <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.ocean FROM '/tmp/ocean.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 24- Operators

```{r operator,echo=TRUE,eval=FALSE}
### Extract spreadsheet 
operator <- readWorksheet(DDD,"OPERATOR")

### Remove second affiliation
### Temporary: Each affiliation should be added in the table
operator <- operator[,c('l_operator','Affiliation1')]

### Save in temp to allow for insertion in the database
write.table(operator,file='/tmp/operator.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.operator
send.references.tables.operator <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.operator FROM '/tmp/operator.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 25- Organic contaminants

```{r organic_contaminants,echo=TRUE,eval=FALSE}
organic_contaminants <- readWorksheet(DDD,"ORGANIC_CONTAMINANTS")

### Save in temp to allow for insertion in the database
write.table(organic_contaminants,file='/tmp/organic_contaminants.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.vessel_storage
send.references.tables.organic_contaminants <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.organic_contaminants FROM '/tmp/organic_contaminants.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 26- Otolith measurement types

```{r otolith_measurement_types,echo=TRUE,eval=FALSE}
otolith_measurement_type <- readWorksheet(DDD,"OTOLITHS")

### Save in temp to allow for insertion in the database
write.table(otolith_measurement_type,file='/tmp/otolith_measurement_type.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.otolith_measurement_type
send.references.tables.otolith_measurement_type <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.otolith_measurement_type FROM '/tmp/otolith_measurement_type.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 27- Packaging types

```{r packaging,echo=TRUE,eval=FALSE}
packaging <- readWorksheet(DDD,"PACKAGING")

### Save in temp to allow for insertion in the database
write.table(packaging,file='/tmp/packaging.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.packaging
send.references.tables.packaging <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.packaging FROM '/tmp/packaging.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 28- Post-ovulatory follicles classification

```{r pof,echo=TRUE,eval=FALSE}
pof <- readWorksheet(DDD,"POF")

### Save in temp to allow for insertion in the database
write.table(pof,file='/tmp/pof.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.pof
send.references.tables.pof <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.pof FROM '/tmp/pof.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 29- Prey groups

```{r prey_groups,echo=TRUE,eval=FALSE}
prey_groups <- readWorksheet(DDD,"PREY_GROUPS")

### Save in temp to allow for insertion in the database
write.table(prey_groups,file='/tmp/prey_groups.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.prey_groups
send.references.tables.prey_groups <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.prey_groups FROM '/tmp/prey_groups.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 30- Processing replicates

```{r processing_replicates,echo=TRUE,eval=FALSE}
processing_replicates <- readWorksheet(DDD,"PROCESSING_REPLICATE")

### Save in temp to allow for insertion in the database
write.table(processing_replicates,file='/tmp/processing_replicates.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.processing_replicate
send.references.tables.processing_replicates <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.processing_replicates FROM '/tmp/processing_replicates.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 31- Projects

```{r project,echo=TRUE,eval=FALSE}
project <- readWorksheet(DDD,"PROJECT")

### Save in temp to allow for insertion in the database
write.table(project,file='/tmp/project.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.project
send.references.tables.project <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.project FROM '/tmp/project.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 32- Sample positions

```{r sample_position,echo=TRUE,eval=FALSE}
sample_position <- readWorksheet(DDD,"SAMPLE_POSITION")

### Save in temp to allow for insertion in the database
write.table(sample_position,file='/tmp/sample_position.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.sample_position
send.references.tables.sample_position <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.sample_position FROM '/tmp/sample_position.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 33- Sampling platforms

```{r sampling_platforms,echo=TRUE,eval=FALSE}
sampling_platform <- readWorksheet(DDD,"SAMPLING_PLATFORM")

### Save in temp to allow for insertion in the database
write.table(sampling_platform,file='/tmp/sampling_platform.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.sampling_platform
send.references.tables.sampling_platform <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.sampling_platform FROM '/tmp/sampling_platform.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 34- Sex classification

```{r sex,echo=TRUE,eval=FALSE}
sex <- readWorksheet(DDD,"SEX")

### Save in temp to allow for insertion in the database
write.table(sex,file='/tmp/sex.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.sex
send.references.tables.sex <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.sex FROM '/tmp/sex.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 35- Species list

```{r species,echo=TRUE,eval=FALSE}
### Caution: Do not include columns 'SFA.ID.ppt' & 'SFA_life_history_table'
species <- readWorksheet(DDD,"SPECIES")[,1:17]

### Save in temp to allow for insertion in the database
write.table(species,file='/tmp/species.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.species
send.references.tables.species <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.species FROM '/tmp/species.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 36- Stomach fullness classification

```{r stomach_fullness,echo=TRUE,eval=FALSE}
stomach_fullness <- readWorksheet(DDD,"STOMACH_FULLNESS")

### Save in temp to allow for insertion in the database
write.table(stomach_fullness,file='/tmp/stomach_fullness.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.stomach_fullness
send.references.tables.stomach_fullness <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.stomach_fullness FROM '/tmp/stomach_fullness.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 37- Storage modes

```{r storage_mode,echo=TRUE,eval=FALSE}
storage_mode <- readWorksheet(DDD,"STORAGE_MODE")

### Save in temp to allow for insertion in the database
write.table(storage_mode,file='/tmp/storage_mode.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.storage_mode
send.references.tables.storage_mode <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.storage_mode FROM '/tmp/storage_mode.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 38- Tissues

```{r tissue,echo=TRUE,eval=FALSE}
tissue <- readWorksheet(DDD,"TISSUE")

### Save in temp to allow for insertion in the database
write.table(tissue,file='/tmp/tissue.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.tissue
send.references.tables.tissue <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.tissue FROM '/tmp/tissue.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 39- Vessels

```{r vessel,echo=TRUE,eval=FALSE}
vessel <- readWorksheet(DDD,"VESSEL")

### Save in temp to allow for insertion in the database
write.table(vessel,file='/tmp/vessel.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.vessel
send.references.tables.vessel <- dbSendQuery(con_emotion3_local,paste0("COPY references_tables.vessel FROM '/tmp/vessel.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```

# 40- Vessel storage classification

```{r vessel_storage,echo=TRUE,eval=FALSE}
### Extract spreadsheet
vessel_storage <- readWorksheet(DDD,"VESSEL_STORAGE")

### Save in temp to allow for insertion in the database
write.table(vessel_storage,file='/tmp/vessel_storage.csv',row.names = FALSE,sep="\t",na = '')

### INSERT references_tables.vessel_storage
send.references.tables.vessel_storage <- dbSendQuery(con_emotion3_local, 
paste0("COPY references_tables.vessel_storage FROM '/tmp/vessel_storage.csv' WITH DELIMITER E'\\t' CSV HEADER"))
```
