---
title: 'BIODATABASE: Loading analysis data'
author: 'Manu Chassot'
date: "`r format(Sys.time(), '%d %B %Y')`"
classoption: 'landscape'
---
  
```{r load_libraries,echo=FALSE,eval=TRUE,results='hide'}
### Install/load devtools
if(!require(devtools)){
  install.packages("devtools", repos = "https://pbil.univ-lyon1.fr/CRAN/")
  suppressPackageStartupMessages(library(devtools,quietly = TRUE))
}

### Install/load lubripack
if(!require(lubripack)){
  install_github("espanta/lubripack")
  suppressPackageStartupMessages(library(lubripack,quietly = TRUE))
}

### Install/load libraries required for analysis
lubripack('RPostgreSQL','knitr','lubridate','openxlsx','data.table',silent = FALSE)
```

```{r document_parameters,echo=FALSE,results='hide',eval=TRUE}
### English
Sys.setlocale("LC_TIME", "en_US.UTF-8")

### PDF/DOC document parameters
knitr::opts_chunk$set(echo = FALSE,tidy.opts=list(width.cutoff=80),tidy=TRUE,size='footnotesize',fig.width=4.5,fig.height=4.5, fig.align = 'center')
```

# Connect to the database

```{r database_connection,echo=TRUE,eval=TRUE}
drv <- dbDriver("PostgreSQL")
con_emotion3_local <-  dbConnect(drv,user="postgres",dbname="emotion3",host="localhost")
```

# Load tracer values

The values of ecological tracers are currently loaded in the database with the Talend job 'load_melting_data' which calls the function melt_analysis_tracers.R that requires as input the list of tracers (analysis_tracers_details.csv) to be inserted in the table analyses_tables.analysis_measures. The list of tracers is generated from the data dictionary design (DDD) loaded in the table metadata.ddd and stored in the table metadata.analysis_tracer_details.

Any addition or removal of tracer in the database will then require the following steps:

1. Update of the spreadsheet DDD from the file 'DDD_database_date.xlsx'. All fields should be entered: entity, tracer_name,	data_type,	unit,	basic_checks,	comment,	tracer,	views_level
2. Loading of the data dictionary in the database with the code 'load_metadata.Rmd' to update the table 'metadata.ddd'
3. Update of the table metadata.analysis_tracer_details with the SQL query embedded within the code load_metadata.Rmd
4. Export of the table 'metadata.analysis_tracer_details' to 'analysis_tracer_details.csv' called by the code 'melt_analysis_tracers.R'
5. The code 'melt_analysis_tracers.R' can be called from the Talend job load_melting_data or from a R console

## Perfluorinated component contaminants 

### Read PFC data from spreadsheet

```{r read_pfc,echo=TRUE,eval=TRUE}
pfc <- fread("../CSV/analysis/Data_Contaminants_PFC.csv")
pfc[, analysis_date := as.POSIXct(analysis_date,format='%d/%m/%Y',tz='SCT')]
```

## Create data set of PFC analysis information

```{r create_pfc_analysis_info,echo=TRUE,eval=FALSE}
pfc_analysis_info <- pfc[, .(analysis_id=talend_an_id,certified_material,pfc_c_unit)]
write.table(pfc_analysis_info,file='/tmp/pfc_analysis_info.csv',row.names = FALSE,sep="\t",na = '')
```

## Insert PFC analysis information data

```{r delete_contents_pfc_analysis_info_before_insertion,echo=TRUE,eval=FALSE}
delete.pfc_analysis <- dbSendQuery(con_emotion3_local,"DELETE FROM analysis_tables.contaminants_pfc")
```

```{r insert_pfc_analysis_info,echo=TRUE,eval=FALSE}
insert.pfc_analysis_info <- dbSendQuery(con_emotion3_local,
paste0("COPY analysis_tables.contaminants_pfc
FROM '/tmp/pfc_analysis_info.csv'
WITH DELIMITER E'\\t' CSV HEADER"))
```

## Add PFC data to analysis table

```{r create_pfc_analysis,echo=TRUE,eval=FALSE}
pfc_analysis <- pfc[, .(analysis_id=talend_an_id,sample_id=subsample_identifier,analysis_type=analysis,analysis_replicate,analysis_lab,analysis_operator=operator_name,analysis_sample_description,analysis_mode,analysis_date,remarks_analysis,data_file_name=NA,analysis_mass=NA,analysis_mass_unit=NA,analysis_date_check=NA)]
write.table(pfc_analysis,file='/tmp/pfc_analysis.csv',row.names = FALSE,sep="\t",na = '')
```

## Insert PFC analysis information data

```{r insert_pfc_analysis,echo=TRUE,eval=FALSE}
insert.pfc_analysis <- dbSendQuery(con_emotion3_local,
paste0("COPY analysis_tables.analysis
FROM '/tmp/pfc_analysis.csv'
WITH DELIMITER E'\\t' CSV HEADER"))
```

```{r disconnect_emotiondb,echo=FALSE,results='hide',include='FALSE'}
dbDisconnect(con_emotion3_local)
```
